The Right Way to Search Evolving Graphs

### 2016-03-04 paper.tex
Fix typo: ocirc -> odot

The simple example of Figure~\ref{fig:eg_shortest_path} demonstrates why sums
over products of adjacency matrices of the form \eqref{eq:sum} do not count
temporal paths correctly: they neglect the combinatorics associated with
the causal edge set $E'$. In the next section, we show how to account for these
causal edges by introducing a new matrix--vector product $\ocirc$.

@@

We see that $(\bm A_n^T)^2$ encodes all the products in
\eqref{eq:5}-\eqref{eq:6}, including both the ordinary matrix--vector product
and the $\ocirc$ product. Furthermore, $(\bm A_3^T)^3 \bm b$ correctly counts the
two allowed temporal paths from $(1, t_1)$ to $(3, t_3)$, and that the
off-diagonal structure encoded in $E'$ and the $M^{[t,t']}$ blocks are critical
to obtaining the correct count.

>>>>

The simple example of Figure~\ref{fig:eg_shortest_path} demonstrates why sums
over products of adjacency matrices of the form \eqref{eq:sum} do not count
temporal paths correctly: they neglect the combinatorics associated with
the causal edge set $E'$. In the next section, we show how to account for these
causal edges by introducing a new matrix--vector product $\odot$.

@@

We see that $(\bm A_n^T)^2$ encodes all the products in
\eqref{eq:5}-\eqref{eq:6}, including both the ordinary matrix--vector product
and the $\odot$ product. Furthermore, $(\bm A_3^T)^3 \bm b$ correctly counts the
two allowed temporal paths from $(1, t_1)$ to $(3, t_3)$, and that the
off-diagonal structure encoded in $E'$ and the $M^{[t,t']}$ blocks are critical
to obtaining the correct count.
